Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium version \YellowPaperVersionNumber{}}}

### 2018-02-08 Paper.tex
\hyperlink{Transaction Receipt} \hyperlink{Pi}{

The values stemming from the computation of transactions, specifically the transaction receipts, $B_{\mathbf{R}}$, and that defined through the transactions state-accumulation function, $\Pi$, are formalised later in section \ref{sec:statenoncevalidation}.

@@

\begin{tabu*} spread 0pt{X[l] X[c] X} \savetabu{col3}
\toprule
Symbol & Latex Command & Description \hypertarget{bigvee}{}\\
\midrule
$\bigvee$ & \verb|\bigvee| & This is the least upper bound, supremum, or join of all elements operated on. Thus it is the greatest element of such elements (\cite{Davey2002_zbMATH01748069}).\\
\bottomrule
\end{tabu*}
\end{document}

>>>>

The values stemming from the computation of transactions, specifically the \hyperlink{Transaction_Receipt}{transaction receipts}, $B_{\mathbf{R}}$, and that defined through the transaction's \hyperlink{Pi}{state-accumulation function, $\Pi$}, are formalised later in section \ref{sec:statenoncevalidation}.

@@

\section{List of mathematical symbols}\label{app:symbols}
\begin{tabu*}{X[l]X[c]X} \savetabu{col3}
\toprule
Symbol & Latex Command & Description \hypertarget{bigvee}{}\\
\midrule
$\bigvee$ & \verb|\bigvee| & This is the least upper bound, supremum, or join of all elements operated on. Thus it is the greatest element of such elements (\cite{Davey2002_zbMATH01748069}).\\
\bottomrule
\end{tabu*}

\end{document}
